The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex
add myself, update section
Add myself to list of authors; add placeholders for TODOs

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Denis Davydov
    Timo Heister
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

@@

The major changes of this release are:
\marginpar{Add one sentence to each of the following.}
\begin{itemize}
\item CellDataStorage class

@@

\item Trilinos linear operators?

\item Physics module

@@

@@

\subsection{Linear operators with Trilinos?}

@@

@@

>>>>

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Denis Davydov,
    Timo Heister,
    Matthias Maier,
    Jean-Paul Pelteret
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[4]{Matthias Maier}
\affil[4]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}

\author[2]{Jean-Paul Pelteret}
\affil[2]{Chair of Applied Mechanics, 
  University of Erlangen-Nuremberg, 
  Egerlandstr.\ 5, 
  91058 Erlangen, 
  Germany.
  {\texttt{jean-paul.pelteret@fau.de}}}

@@

The major changes of this release are:
\marginpar{Add one sentence to each of the following.}
\begin{itemize}
\item CellDataStorage class
  TODO: Denis and Jean-Paul

@@

\item Trilinos linear operators?
  TODO: Jean-Paul and Matthias

\item Physics module
  TODO: Denis and Jean-Paul

@@

TODO: Denis and Jean-Paul

@@

\subsection{TODO: Linear operators with Payload and Trilinos}

TODO: Jean-Paul and Matthias

@@

TODO: Jean-Paul

@@

J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
